mouse level quality plots

### 2019-09-26 doc/MouseLevelPlots.Rmd
updating list of mice to finish
ran mouse level plots with new batch16 data

#load main data file
load(file="data/MLH1/MLH1_data_setup_8.29.19.RData")#batch15 isn't showing up
#load(file="data/MetaData.RData")#this Rdata was replacing the most current batch.. agg!

@@

df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
#this is where you remove the non-data data!
df_list <- df_list[ -c(7,12,14,18,20,21,22,24,26,28,30) ]

#7 PERC, 12 MOLF female, 
#

>>>>

#load main data file
load(file="data/MLH1/MLH1_data_setup_9.26.19.RData")#added batch16
#load(file="data/MLH1/MLH1_data_setup_8.29.19.RData")#batch15 isn't showing up
#load(file="data/MetaData.RData")#this Rdata was replacing the most current batch.. agg!

@@

df_list <- split(MLH1_data, (MLH1_data$category))
#remove sections which are in category but have no data
#this is where you remove the non-data data!
df_list <- df_list[ -c(12,18,24,30) ]
#there is PERC male

#12 MOLF female, 18 CZECH female, 24 HMI female?, 
#
